Title

### 2023-10-21 Response to Reviewers.tex

 \item  \textbf{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?} \\

 We added a couple of sentences talking about that.

 \item \textbf{Imprcise} \\

 \item \textbf{This reasoning I miss, simplifying for achieving what goal? }

 \item\textbf{ There is no quantification of this, it´s not even the focus of the paper.}

 \item \textbf{Citation required here.}
 I placed a citation.
\end{enumerate}

### 2023-10-21 main.tex
Articulo

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two main
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, since the quantum computer ibmq-lima we used does not have that many qubits,
we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}b.

@@

\tbnote{Añadir un parrafito al final que lo visualizamos sólo para una dimensión,
pero que para más dimensiones creemos que los mapas representativos se podrán hacer así. 
Sería interesante verlo en el futuro.}

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise. Responder que 
esperamos que ya con los cambios hechos esté más claro}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities.

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. \revnote{This reasoning I miss, simplifying for achieving what goal? } 
\tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
\tbnote{Given this condition, we considered the space of Pauli maps that are possible to parametrize with one parameter, and 
gave some explicit examples for a system of one qubit. 
We expect that as the number of qubits gets bigger, the space of such maps becomes a smaller 
part of the whole space of Pauli dynamical maps. 
However, some paradigmatic maps as the dephasing one we studied for 2 qubits will still be
possible to do with a 1PR circuit (for this case, this can be seen by
noticing that said dephasing channel in \eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo}, which we proved
to be possible to implement with a 1PR circuit).}

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the effect that the error of a quantum computer have
on these simulations, quantified by the fidelity. \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning~\cite{Benedetti}.

>>>>

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}
\label{2qbit}
For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two main
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, since the quantum computer ibmq-lima we used does not have that many qubits,
we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}b.

@@

\tbnote{Añadí el párrafo en verde hablando de eso.}

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities.

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. \revnote{This reasoning I miss, simplifying for achieving what goal? } 
\tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
\tbnote{Given this condition, we considered the space of Pauli maps that are possible to parametrize with one parameter, and 
gave some explicit examples for a system of one qubit. 
As the number of qubits gets bigger, the degrees of freedom for choosing a Pauli dynamical map also gets bigger,
so we would expect that the space of maps that can be done with only 
one parameter
becomes a smaller part of the whole space of Pauli dynamical maps.
However, some paradigmatic maps as the dephasing one we studied for 2 qubits in section \ref{2qbit} will still be
possible to do with a 1PR circuit (for this case, this can be seen by
noticing that said dephasing channel in \eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo}, which we proved
to be possible to implement with a 1PR circuit).}

In conclusion, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the effect that the error of a quantum computer have
on these simulations, quantified by the fidelity. \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning~\cite{Benedetti}.
